### 2018-01-11 derivations.tex
add temporary product based fall / chem forms?

The derivatives of the unimolecular\slash~recombination fall-off reaction third-body pressure modification term are:
\begin{align}
 \lhs{dci_fall}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial T } + \frac{\partial P_{r, i} }{\partial T } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{,} \label{e:dci_fall_dt}\\
 \lhs{dci_fall}{\frac{\partial c_{i} }{\partial n_j}} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial n[j] } + \frac{\partial P_{r, i} }{\partial n_j } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{,} \label{e:dci_fall_dnj}
\end{align}
and with respect to the thermodynamic parameter:
\begin{subequations}
 \label{e:dci_fall_de}
 \begin{align}
  \lhs{dci_fall}{\frac{\partial c_i }{\partial V }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial V } + \frac{\partial P_{r, i} }{\partial V } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{\dconp} \\
  \lhs{dci_fall}{\frac{\partial c_i }{\partial P }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial P } + \frac{\partial P_{r, i} }{\partial P } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{\dconv}
 \end{align}
\end{subequations}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

The derivatives of the unimolecular\slash~recombination fall-off reaction third-body pressure modification term are:
\begin{align}
 \label{e:dci_fall_dt}
 \lhs{dci_fall}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial T } + \frac{\partial P_{r, i} }{\partial T } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{,}\\
 \label{e:dci_fall_dnj}
 \lhs{dci_fall}{\frac{\partial c_{i} }{\partial n_j}} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial n[j] } + \frac{\partial P_{r, i} }{\partial n_j } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{,}
\end{align}
and with respect to the thermodynamic parameter:
\begin{subequations}
 \label{e:dci_fall_de}
 \begin{align}
  \lhs{dci_fall}{\frac{\partial c_i }{\partial V }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial V } + \frac{\partial P_{r, i} }{\partial V } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{\dconp} \\
  \lhs{dci_fall}{\frac{\partial c_i }{\partial P }} &= \rhs{dci_fall}{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial P } + \frac{\partial P_{r, i} }{\partial P } \left(F_{i} - c_{i}\right)\right)} & \cond{dci_fall}{\dconv}
 \end{align}
\end{subequations}

@@

\label{e:dfi_lind_dt_prod}

@@

\label{e:dfi_lind_dnj_prod}

@@

 \label{e:dfi_lind_de_prod}

@@

\label{e:dfi_troe_dt_prod}

@@

\label{e:dfi_troe_dnj_prod}

@@

 \label{e:dfi_troe_de_prod}

@@

 \label{e:dfi_sri_dt_prod}

@@

 \label{e:dfi_sri_dnj_prod}

@@

 \label{e:dfi_sri_de_prod}

@@

\subsubsection{Unimolecular\slash~recombination fall-off reactions (temporary product form)}
Using the temporary products developed in~\cref{s:dpr,s:dfi}, the fall-off reaction derivatives developed in~\cref{e:dci_fall_dt,e:dci_fall_dnj,e:dci_fall_de} may be simplified to:
\begin{align}
\lhs{dci_fall_complete}{\frac{\partial c }{\partial T }_{i}} &= \rhs{dci_fall_complete}{\frac{F_{i} \bar{\theta}_{P_{r, i}, \partial T}}{P_{r, i} + 1} + \biggl(- \frac{P_{r, i} \Theta_{P_{r,i}, \partial T}}{P_{r, i} + 1} + \Theta_{F_i, \partial T} + } & \nonumber \\
							     &  \rhs{dci_fall_complete}{\mathindent[largerindentpleas] \Theta_{P_{r,i}, \partial T} - \frac{\bar{\theta}_{P_{r, i}, \partial T}}{P_{r, i} + 1}\biggr) c_{i}} & \cond{dci_fall_complete}{,} \\
\lhs{dci_fall_complete}{\frac{\partial c }{\partial {n_j} }_{i}} &= \rhs{dci_fall_complete}{\frac{k_{0, i} \bar{\theta}_{P_{r, i}, \partial n_j}}{V k_{\infty, i} \left(P_{r, i} + 1\right)} \left(F_{i} \left(P_{r, i} \Theta_{F_i, \partial n_j} + 1\right) - c_{i}\right)} & \cond{dci_fall_complete}{,}
\end{align}
and:
\begin{subequations}
 \begin{align}
  \lhs{dci_fall_complete}{\frac{\partial c }{\partial V }_{i}} &= \rhs{dci_fall_complete}{\frac{F_{i} \bar{\theta}_{P_{r, i}, \partial V}}{P_{r, i} + 1} + \biggl(- \frac{P_{r, i} \Theta_{P_{r,i}, \partial V}}{P_{r, i} + 1} + \Theta_{F_i, \partial V} + } & \nonumber \\
							       &  \rhs{dci_fall_complete}{\mathindent[largerindentpleas] \Theta_{P_{r,i}, \partial V} - \frac{\bar{\theta}_{P_{r, i}, \partial V}}{P_{r, i} + 1} \biggr) c_{i}} & \cond{dci_fall_complete}{\dconp} \\
  \lhs{dci_fall_complete}{\frac{\partial c }{\partial P }_{i}} &= \rhs{dci_fall_complete}{\frac{F_{i} \bar{\theta}_{P_{r, i}, \partial P}}{P_{r, i} + 1} + \left(\Theta_{F_i, \partial P} - \frac{\bar{\theta}_{P_{r, i}, \partial P}}{P_{r, i} + 1}\right) c_{i}} & \cond{dci_fall_complete}{\dconv}
 \end{align}
\end{subequations}
where the temporary products are given by~\cref{e:dpr_theta_dt,e:dpr_theta_bar_dt,e:dpr_theta_bar_dnj,e:dpr_theta_dv,e:dpr_theta_bar_dv,e:dpr_theta_dp}~and~\cref{e:dfi_lind_dt_prod,e:dfi_lind_dnj_prod,e:dfi_lind_de_prod,e:dfi_troe_dt_prod,e:dfi_troe_dnj_prod,e:dfi_troe_de_prod,e:dfi_sri_dt_prod,e:dfi_sri_dnj_prod,e:dfi_sri_de_prod}

\subsubsection{Chemically-activated bimolecular reactions (temporary product form)}
Similarly, the chemically-activated reaction derivatives in~\cref{e:dci_chem_dt,e:dci_chem_dnj,e:dci_chem_de} may be written as:
\begin{align}
\lhs{dci_chem_complete}{\frac{\partial c }{\partial T }_{i}} &= \rhs{dci_chem_complete}{\left(- \frac{P_{r, i} \Theta_{P_{r,i}, \partial T}}{P_{r, i} + 1} + \Theta_{F_i, \partial T} - \frac{\bar{\theta}_{P_{r, i}, \partial T}}{P_{r, i} + 1}\right) c_{i}} & \cond{dci_chem_complete}{,} \\
\lhs{dci_chem_complete}{\frac{\partial c }{\partial {n_j} }_{i}} &= \rhs{dci_chem_complete}{\frac{k_{0, i} \bar{\theta}_{P_{r, i}, \partial n_j} \left(F_{i} \Theta_{F_i, \partial n_j} - c_{i}\right)}{k_{\infty, i} V \left(P_{r, i} + 1\right)}} & \cond{dci_chem_complete}{,}
\end{align}
and:
\begin{subequations}
 \begin{align}
  \lhs{dci_chem_complete}{\frac{\partial c }{\partial V }_{i}} &= \rhs{dci_fall_complete}{\left(- \frac{P_{r, i} \Theta_{P_{r,i}, \partial V}}{P_{r, i} + 1} + \Theta_{F_i, \partial V} - \frac{\bar{\theta}_{P_{r, i}, \partial V}}{P_{r, i} + 1}\right) c_{i}} & \cond{dci_chem_complete}{\dconp} \\
  \lhs{dci_chem_complete}{\frac{\partial c }{\partial P }_{i}} &= \rhs{dci_fall_complete}{\left(\Theta_{F_i, \partial P} - \frac{\bar{\theta}_{P_{r, i}, \partial P}}{P_{r, i} + 1}\right) c_{i}} & \cond{dci_chem_complete}{\dconv}
 \end{align}
\end{subequations}
